Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-21 paper.tex
fix table I to just use case MI values - to avoid complicated discussion of why selected params are different between table I and III.

\begin{table}[h]
    \caption{Reactor Facility Parameters}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
            & LWR & SFR \\
        \hline                       
        Lifetime (yr)         & 80 & 80 \\
        Cycle length (months) & 18 & 15 \\
        Batch size (kg)       & 29565 & 7490 \\
        Batches per core      & 3 & 5 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \label{tab:reactors}
\end{table}

The described scenario is used as closely as possible in each of the four
cases.  However, a few small case-dependent changes to the scenarios relating to
reactor configuration are necessary.
The invariants preserved with respect to reactor behavior between all
four cases are shown in Table \ref{tab:invar}.  Table \ref{tab:reactor-detail} shows
the computed/selected configuration for both LWR and SFR reactor types for all
four cases.

@@

The value of realism in fuel cycle modeling is greatly be enhanced by an
associated understanding of how outcomes are affected by added fidelity.
Cyclus' flexibility for accommodating different modeling choices uniquely
enables many interesting comparisons.  Continued work in this direction has
great potential to to improve the integrity of fuel cycle analysis generally.

>>>>

\begin{table}[h]
    \caption{Reactor Facility Parameters}
    \centering
    \begin{tabular}{ |r | c c | }
        \hline                       
            & LWR & SFR \\
        \hline                       
        Lifetime (yr)         & 80 & 80 \\
        Cycle length (months) & 18 & 15 \\
        Batch size (kg)       & 29565 & 8025 \\
        Batches per core      & 3 & 5 \\
        \hline                       
    \end{tabular}
    \captionsetup{justification=centering}
    \label{tab:reactors}
\end{table}

The described scenario is used as closely as possible in each of the four
cases with appropriate adjustments for case-specific differences (e.g. monthly
vs. quarterly time steps).  Invariants preserved with respect to reactor
behavior between all four cases are shown in Table \ref{tab:invar}.  Table
\ref{tab:reactor-detail} shows the computed/selected configuration for both
LWR and SFR reactor types that was used in Cyclus input files for all four
cases.

@@

The value of realism in fuel cycle modeling is greatly be enhanced by an
associated understanding of how outcomes are affected by added fidelity.
Cyclus' flexibility for accommodating different modeling choices uniquely
enables many interesting comparisons.  Those in the field of fuel cycle
analysis in general should be cognizant of how modeling choices are affecting
results and conclusions through exercises like the one here.  Even if the
outcome is that a particular modeling decision has little impact on results,
work in this direction has great potential to improve the integrity of fuel
cycle analysis generally.
